Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-17 Docs/TODAES/paper.tex
Fixed References and Libraries

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}
\usepackage[skip=\baselineskip]{caption}
\captionsetup[lstlisting]{font={normalsize,tt}}

\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}

\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Copyright
\setcopyright{rightsretained}

@@

\lstset{language=C,basicstyle=\small}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
\lstset{tabsize=2}
\lstset{firstnumber=1}
\lstset{frame=single}
\lstset{
  language={C},
  morekeywords={assert,uchar}
}

@@

\begin{lstlisting}[caption=OpenMP basic example.]
int i;
#pragma omp parallel for
for (i = 0; i < 10; i++)
  a[i] = 2 * i;
\end{lstlisting}

@@

\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
(declare-const K Int) 
(declare-const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

@@

\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
 Initialize Variables 
 Declare number of nodes and edges
 Declare hardware cost of each node as array (h)
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare the initial software cost of ($S_{0}$)
 Declare transposed incidence matrix graph G (E)
 Define the solutions variable ($X_{i}$ ) as Boolean
 main {
  for TipH = 0 to Hmax do {
   populate $X_{i}$ with nondeterministic/test values
   Calculate s(1-x)+c|$E_{x}$| and store at variable
   Requirement isued by Assume (Variable <= $S_{0}$)
   Calculate Hp cost Based on value tested of $X_{i}$
   Violation check with Assert($H_{p}$ > TipH)
  }
 }
\end{lstlisting}

@@

Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.

\begin{lstlisting}[caption=Steps calculation using intervals.,label=Steps-Calculation-using-Intervals]
 GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
     if(chunk.right - chunk.left > largestChunk){
           largestChunk = chunk.right - chunk.left;
           largest = chunk;
     }
   }	
   chunks.remove(largest);	
   int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
      if(largest.right - largest.left > 1)
         chunks.add(new chunk(largest.left, median - 1));	
      if(largest.right != largest.left)
         chunks.add(new chunk(median + 1, largest.right);
    }
   return median;
 }
\end{lstlisting}

@@

\begin{lstlisting}[caption=Worker sample.,label=worker-sample]
 step = controller.GetNextStep();
 int pid = ExecuteStep(step);
 while(isRunning(pid)){
   if(!controller.isNeeded(step))
    kill(pid);
 }     
\end{lstlisting}

@@

\begin{lstlisting}[caption=Pseudocode describing ESBMC-$\nu$Z.,label=vZ-pseudocode, mathescape]
#Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_{0}$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G (E)
#Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
#Assert Constraints
  Add constraints (SF + CMC <= $S_{0}$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

@@

\begin{table}[h]
\centering
\caption {Description of Benchmarks.}
\small
\sffamily\small
\tabulinesep=6pt
\begin{tabular}[c]{m{1.9cm}m{0.9cm}m{0.9cm}m{9.0cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\end{tabular}
\label{Description-of-Benchmarks}
\end{table}

@@

%----------------------------------------------
%\section{References}
%\label{References}
%----------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%
% ---- Bibliography ---- %
%%%%%%%%%%%%%%%%%%%%%%%%%%

% Bibliography
\begin{thebibliography}{5}

\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\eprint}[2][]{\url{#2}}
\bibliographystyle{ACM-Reference-Format-Journals}

%1
\bibitem{Arato2003}
Arat\'o, P., Juh\'asz, S., Mann, Z.A., Orb\'an, A., Papp, D. (2003), ``{Hardware/software partitioning in embedded system design},'' In: Proc. of the Intl. Symp. of Intelligent Signal Processing, pp. 192--202.

%2
\bibitem{Mann2007}
Mann, Z.A., Orb\'an, A., Arat\'o, P., ``{Finding optimal hardware/software partitions},'' In: Formal Methods in System Design, v. 31, n. 3 pp. 241--263.

%3
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
\bibitem{Trindade2016}
Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.

%7
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org%

%8
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%9
\bibitem{Rao2009}
Rao, S. (2009), ``{Engineering Optimization: Theory and Practice. 4th edition}'', John Wiley \& Sons, Hoboken.

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.

%11
\bibitem{Clarke2001}
E. M. Clarke, A. Biere, R. Raimi, Y. Zhu (2001), ``{Bounded model checking using satisfiability solving}'', Formal Methods in System Design v. 19 n. 1, pp. 7--34.

%12
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl. Journal on Software Tools for Technology Transfer, v. 11, n. 1, pp. 69--83.

%13
\bibitem{Ganai2006}
Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.

%14
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl. Conf. and Workshops on the Engineering of Computer-Based Systems, pp. 147--156.

%15
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.

%16
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp. 174-–177.

%17
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 6806, pp. 171--177.

%18
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v. 35, n. 1-3, pp. 265--293.

%19
\bibitem{Dutertre2014}
Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.

%20
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc. of the Intl. Conf. on Software Engineering and Service Science, pp. 921--924.

%21
\bibitem{Bjorner2014}
Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.

%22
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc. of the Intl. Conf. on Service-Oriented Computing, LNCS 5364, pp. 116--131

%23
\bibitem{NarodytskaN}
Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.

%24
\bibitem{Barth1995}
Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.

%25
\bibitem{Vasco2005}
Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.

%26
\bibitem{Z3API}
Magellan, ``{Source code and documentation},''
  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.

%27
\bibitem{Cormem}
Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.

%28
\bibitem{Dagum1998}
Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.

%29
\bibitem{TheMathWorks2013}
The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.

%30
\bibitem{Tranquillo2011}
Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.

%31
\bibitem{Hong2010}
Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc. of the Intl. Conf. on Computer and Automation Engineering, pp. 185--189.

%32
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.

%33
\bibitem{Teich2012}
Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.

%34
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc. of the annual workshop on workload characterization, pp. 3--14.

%35
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.

%36
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.

%37
\bibitem{Holzmann2012}
Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.

%38
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.

%39
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc. of the Intl. Symp. on Parallel \& Distributed processing, pp. 1049--1058.

%40
\bibitem{Pavlinovic2015}
Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.

%41
\bibitem{Patrick2015}
Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.

%42
\bibitem{Holzmann11}
Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.

\end{thebibliography}

% Appendix
%\appendix
%\section*{APPENDIX}
%\setcounter{section}{1}
%In this appendix, we measure
%the channel switching time of Micaz [CROSSBOW] sensor devices.
%In our experiments, one mote alternatingly switches between Channels
%11 and 12. Every time after the node switches to a channel, it sends
%%out a packet immediately and then changes to a new channel as soon
%as the transmission is finished. We measure the
%number of packets the test mote can send in 10 seconds, denoted as
%$%N_{1}$. In contrast, we also measure the same value of the test
%mote without switching channels, denoted as $N_{2}$. We calculate
%the channel-switching time $s$ as
%\begin{eqnarray}%
%s=\frac{10}{N_{1}}-\frac{10}{N_{2}}. \nonumber
%\end{eqnarray}%
%By repeating the experiments 100 times, we get the average
%channel-switching time of Micaz motes: 24.3$\mu$s.

%\appendixhead{ZHOU}

% Acknowledgments
%\begin{acks}
%The authors would like to thank Dr. Maura Turolla of Telecom
%Italia for providing specifications about the application scenario.
%\end{acks}

% Bibliography
% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\bibliography{acmsmall-sample-bibfile}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
%\received{February 2007}{March 2009}{June 2009}

% Electronic Appendix
%\elecappendix

%\medskip

%\section{This is an example of Appendix section head}

%Channel-switching time is measured as the time length it takes for
%motes to successfully switch from one channel to another. This
%parameter impacts the maximum network throughput, because motes
%cannot receive or send any packet during this period of time, and it
%also affects the efficiency of toggle snooping in MMSN, where motes
%need to sense through channels rapidly.

%By repeating experiments 100 times, we get the average
%channel-switching time of Micaz motes: 24.3 $\mu$s. We then conduct
%the same experiments with different Micaz motes, as well as
%experiments with the transmitter switching from Channel 11 to other
%channels. In both scenarios, the channel-switching time does not have
%obvious changes. (In our experiments, all values are in the range of
%23.6 $\mu$s to 24.9 $\mu$s.)

%\section{Appendix section head}

%The primary consumer of energy in WSNs is idle listening. The key to
%reduce idle listening is executing low duty-cycle on nodes. Two
%primary approaches are considered in controlling duty-cycles in the
%MAC layer.

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

>>>>

\documentclass[prodmode,acmtrets]{acmsmall} % Aptara syntax

\usepackage{listings} % Codes
%\lstset{
 % language=C,                % choose the language of the code
 % numbers=left,                   % where to put the line-numbers
 % stepnumber=1,                   % the step between two line-numbers.        
 % numbersep=5pt,                  % how far the line-numbers are from the code
 % backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
 % showspaces=false,               % show spaces adding particular underscores
 % showstringspaces=false,         % underline spaces within strings
 % showtabs=false,                 % show tabs within strings adding particular underscores
 % tabsize=2,                      % sets default tabsize to 2 spaces
 % captionpos=b,                   % sets the caption-position to bottom
 % breaklines=true,                % sets automatic line breaking
 % breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
 % title=\lstname,                 % show the filename of files included with \lstinputlisting;
%}

\usepackage{mathtools} % Serve para as equacoes

%Montar os Gráficos, cores e divisões.
\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}  
\usepackage{tabularx} % in the preamble
\usepackage{graphicx} %Imagens

\usepackage{minted}
\newcolumntype{C}[1]{>{\Centering}m{#1}}
\renewcommand\tabularxcolumn[1]{C{#1}}
\usepackage{tabularx,ragged2e,booktabs,caption}

%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial

\usepackage{hyphenat}
\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

%\usepackage[skip=\baselineskip]{caption}
%\captionsetup[lstlisting]{font={small,tt}}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2015}
\acmMonth{3}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
int i;
#pragma omp parallel for
for (i = 0; i < 10; i++)
a[i] = 2 * i;
\end{minted}
\caption{OpenMP basic Example.}
\label{lst:example}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{minted}
\caption{Example of SMT formula using $\nu$Z.}
\label{vZ}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
 Initialize Variables 
 Declare number of nodes and edges
 Declare hardware cost of each node as array (h)
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare the initial software cost of (S0)
 Declare transposed incidence matrix graph G (E)
 Define the solutions variable (Xi) as Boolean
 main {
  For TipH = 0 to Hmax Do {
   populate Xi with nondeterministic/test values
   Calculate s(1-x)+c|Ex| and store at variable
   Requirement isued by Assume (Variable <= S0)
   Calculate Hp cost Based on value tested of Xi
   Violation check with Assert(Hp > TipH)
  }
 }
\end{minted}
\caption{Pseudocode describing sequential ESBMC}
\label{Pseudocode-describing-ESBMC}
\end{listing}

@@

Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
  GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
     if(chunk.right - chunk.left > largestChunk){
           largestChunk = chunk.right - chunk.left;
           largest = chunk;
     }
   }	
   chunks.remove(largest);	
   int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
      if(largest.right - largest.left > 1)
         chunks.add(new chunk(largest.left, median - 1));	
      if(largest.right != largest.left)
         chunks.add(new chunk(median + 1, largest.right);
    }
   return median;
 }
\end{minted}
\caption{Steps calculation using intervals.}
\label{Steps-Calculation-using-Intervals}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
 step = controller.GetNextStep();
 int pid = ExecuteStep(step);
 while(isRunning(pid)){
   if(!controller.isNeeded(step))
    kill(pid);
 }
\end{minted}
\caption{Worker sample.}
\label{worker-sample}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and S0
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G (E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= S0)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{minted}
\caption{Pseudocode describing ESBMC-$\nu$Z.}
\label{vZ-pseudocode}
\end{listing}

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} \label{tab:Description-of-Benchmarks} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\end{tabular}\par
\bigskip
\end{minipage}

%\begin{table}[h]
%\centering
%\caption {Description of Benchmarks.}
%\small
%\sffamily\small
%\tabulinesep=6pt

%\label{Description-of-Benchmarks}
%\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
% ---- Bibliography ---- %
%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{Ref.bib}

\end{document}
